### 2024-09-12 AISTAT25/aistats.tex
updated figures
Made some changes to experimental section

\begin{figure}
\begin{center}
\includegraphics[width=3in]{ideas.pdf}
\end{center}
\caption{(a) A collection of balls $\B$. Ball $B$ has bias $\yh(B) \in \{-1,0,+1\}$. (b) If one ball has bias $+1$ and the other $-1$, points in their intersection are targeted for active querying. (c) Biases of progressively smaller balls containing $x$ might flip sign, leading to \emph{mind changes} about the label of $x$.}
\label{fig:challenges}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=2.5in]{oned-monotonic.pdf}
%\hspace{.5in}
\includegraphics[width=2.5in]{oned-massart.pdf}
\end{center}
\caption{(a) The conditional probability function $\eta$ is monotonically increasing; $\eta(x) = -\gamma, 0, \gamma$ at $x = \lambda_L, \lambda, \lambda_R$, respectively. (b) On each subinterval, $\eta$ is either $> \gamma$ or $<-\gamma$.}
\label{fig:oned}
\end{figure}

@@

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=3in]{figures/ideas.pdf}
\end{center}
\caption{(a) A collection of balls $\B$. Ball $B$ has bias $\yh(B) \in \{-1,0,+1\}$. (b) If one ball has bias $+1$ and the other $-1$, points in their intersection are targeted for active querying. (c) Biases of progressively smaller balls containing $x$ might flip sign, leading to \emph{mind changes} about the label of $x$.}
\label{fig:challenges}
\end{figure}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=2.5in]{figures/Monotone.png}
%\hspace{.5in}
\includegraphics[width=2.5in]{figures/Massart.png}
\end{center}
\caption{(a) The conditional probability function $\eta$ is monotonically increasing; $\eta(x) = -\gamma, 0, \gamma$ at $x = \lambda_L, \lambda, \lambda_R$, respectively. (b) On each subinterval, $\eta$ is either $> \gamma$ or $<-\gamma$.}
\label{fig:oned}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=3in]{figures/MassartExperiment.png}
\end{center}
\caption{{\bf Experimental evidence:} This figure compares the performance of passive sampling alone to that of the active learning algorithm. The X axis represents the number of queries made and the Y axis represents the difference between the error achieved and the optimal achievable error. }
\label{fig:Experiments}
\end{figure}

\section{Experiments}

We provide experimental evidence that our algorithm works. We chose a simple 1D problem, described in figure~\ref{}. Although this problem is simple, it is outside the scope of algorithms that assume that the conditional probability is smooth.

\section{Future Directions}
